---
title: "street barriers"
author: "Emily McCarthy"
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This notebook...

## Dependencies
This notebook requires...

```{r load-packages}
# tidyverse packages
library(dplyr)
library(stringr)
library(tibble)
library(fuzzyjoin)
library(readr)
library(tidyr)

# other packages
library(here)
library(sf)
library(janitor)
library(naniar)
```

## Load Data
This notebook requires these data:

```{r load-data}
RAW_ADDRESS <- st_read(here("data", "pargeocd", "pargeocd.shp"), stringsAsFactors = FALSE)
CENSUS <- st_read(here("data", "tl_2018_29510_addrfeat", "tl_2018_29510_addrfeat.shp"), stringsAsFactors = FALSE)
```

## Part 1
I will first attempt to find missing varibales in the census data. 

```{r p1-q1}
miss_var_summary(CENSUS)
```

I will now combine the two columns of address data in `RAW_ADDRESSES` to include streetname and street type in the same column. 

```{r}
RAW_ADDRESS %>%
  mutate(COMPLETESTREET = str_c(STREETNAME, STREETTYPE, sep = " ")) -> ADDRESSES

ADDRESSES %>%
  select(HANDLE, HOUSENUM, UNITNUM, COMPLETESTREET, ZIP, PARCELID, CITYBLOCK, PARCEL, ADDRRECNUM ) -> ADDRESSES
```

I will now determine if ADDRECNUM is a unique column variable. 

I will now rename one of the variables in `CENSUS_ADDRESS`

```{r}
CENSUS %>%
  rename(
    COMPLETESTREET = FULLNAME
  ) -> CENSUS
```

I will now select only necessary columns

```{r}
CENSUS %>%
mutate(toupper(CENSUS$COMPLETESTREET)) -> CENSUS 
```

Reformatting data tables

```{r}
CENSUS %>%
  select(-COMPLETESTREET) %>%
  rename(COMPLETESTREET = `toupper(CENSUS$COMPLETESTREET)`) -> CENSUS_CLEAN
```


I will now join these tables. 
First I will set geometry to NULL

```{r}
#st_geometry(CENSUS_CLEAN) <- NULL

```

```{r}
JOINED_ADDRESS <- fuzzy_left_join(CENSUS_CLEAN, ADDRESSES,
                                  by = c(
                                    "COMPLETESTREET" = "COMPLETESTREET"),
                                  match_fun = list(`==`))
```

by = c(
                        "number" = "rightLow",
                        "number" = "leftHigh",
                        "street" = "street"
                    ),
                    match_fun = list(`>=`, `<=`, `==`) )


```{r}
JOINED_ADDRESS <- 
```


