---
title: "street barriers"
author: "Emily McCarthy"
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This notebook...

## Dependencies
This notebook requires...

```{r load-packages}
# tidyverse packages
library(dplyr)
library(stringr)
library(tibble)
library(fuzzyjoin)
library(readr)
library(tidyr)

# other packages
library(here)
library(sf)
library(janitor)
library(naniar)
```

## Load Data
This notebook requires these data:

```{r load-data}
RAW_ADDRESS <- st_read(here("data", "pargeocd", "pargeocd.shp"), stringsAsFactors = FALSE)
CENSUS <- st_read(here("data", "tl_2018_29510_addrfeat", "tl_2018_29510_addrfeat.shp"), stringsAsFactors = FALSE)
```

## Part 1
I will first attempt to find missing varibales in the census data. 

```{r p1-q1}
miss_var_summary(CENSUS)
```

I will now combine the two columns of address data in `RAW_ADDRESSES` to include streetname and street type in the same column. 

```{r}
RAW_ADDRESS %>%
  mutate(COMPLETESTREET = str_c(STREETNAME, STREETTYPE, sep = " ")) -> ADDRESSES

ADDRESSES %>%
  select(HANDLE, HOUSENUM, UNITNUM, COMPLETESTREET, ZIP, PARCELID, CITYBLOCK, PARCEL, ADDRRECNUM ) -> ADDRESSES
```

I will now determine if ADDRECNUM is a unique column variable. 

I will now rename one of the variables in `CENSUS_ADDRESS`

```{r}
CENSUS %>%
  rename(
    COMPLETESTREET = FULLNAME
  ) -> CENSUS
```

I will now select only necessary columns

```{r}
CENSUS %>%
mutate(toupper(CENSUS$COMPLETESTREET)) -> CENSUS 
```

Reformatting data tables

```{r}
CENSUS %>%
  select(-COMPLETESTREET) %>%
  rename(COMPLETESTREET = `toupper(CENSUS$COMPLETESTREET)`) -> CENSUS_CLEAN
```


I will now join these tables. 
First I will set geometry to NULL

```{r}
#st_geometry(CENSUS_CLEAN) <- NULL

# FULL_JOINED_ADDRESS <- drop_na(JOINED_ADDRESS)
CENSUS_CLEAN %>%
  mutate(LFROMHN = ifelse(is.na(LFROMHN) == TRUE, 0, LFROMHN)) %>%
  mutate(LTOHN = ifelse(is.na(LTOHN) == TRUE, 0, LTOHN)) %>%
  mutate(RFROMHN = ifelse(is.na(RFROMHN) == TRUE, 0, RFROMHN)) %>%
  mutate(RTOHN= ifelse(is.na(RTOHN) == TRUE, 0, RTOHN))%>%
  select(-LFROMTYP, -LTOTYP, -RFROMTYP, -RTOTYP, -PARITYL, -PARITYR, -ZIPL, -ZIPR, -ARIDL, -ARIDR, -PLUS4L, -PLUS4R, -EDGE_MTFCC, -ROAD_MTFCC, -OFFSETL, -OFFSETR) -> Census_drop

```

```{r}
ADDRESSES %>%
 filter(is.na(UNITNUM) == TRUE) %>%
  mutate(HOUSENUM = as.numeric(HOUSENUM)) -> ADDRESSES
Census_drop %>%
  mutate(LFROMHN = as.numeric(LFROMHN)) %>%
  mutate(RTOHN = as.numeric(RTOHN)) -> Census_drop
```

```{r}
JOINED_ADDRESS <- fuzzy_left_join(ADDRESSES, Census_drop,
                                  by = (c(
                                 "LFROMHN" = "HOUSENUM",
                                  "LTOHN" = "HOUSENUM",
                                  "COMPLETESTREET" = "COMPLETESTREET")),
                                  match_fun = list(`<=`, `>=`, `==`))
```

```{r}
JOINED_LEFT <- fuzzy_left_join(Census_drop, ADDRESSES,
                                  by = as.numeric(c(
                                    "LFROMHN" = "HOUSENUM",
                                    "LTOHN" = "HOUSENUM",
                                    "COMPLETESTREET" = "COMPLETESTREET")),
                                  match_fun = list(`<=`, `>=`, `==`))
```

by = c(
                        "number" = "rightLow",
                        "number" = "leftHigh",
                        "street" = "street"
                    ),
                    match_fun = list(`>=`, `<=`, `==`) )


```{r}
# JOINED_ADDRESS <- select(JOINED_ADDRESS, -PLUS4L, -PLUS4R)
JOINED_ADDRESS <- select(JOINED_ADDRESS, -LFROMTYP, -LTOTYP, -RFROMTYP, -RTOTYP, -PARITYL, -PARITYR)

```

```{r}
slice(Census_drop, 1:150) -> slice
```

```{r}
slice(ADDRESSES, 1:150) -> address_slice
```

```{r}
JOINED_LEFT_slice <- fuzzy_left_join(ADDRESSES, slice,
                                  by = c(
                                    "HOUSENUM" = "LFROMHN",
                                    "HOUSENUM" = "LTOHN",
                                    "COMPLETESTREET" = "COMPLETESTREET"),
                                  match_fun = list(`>=`, `<=`, `==`))
```

